Theory of Phonon Polaritons in Polar Dielectrics

### 2018-08-05 paper.tex
More edits.

The way to proceed on all of these questions is an \emph{ab initio} framework to predict the phonon contribution to the dielectric tensor in arbitrary settings. Frameworks exist for calculating the local permittivity coming from phonons in a 3D bulk, as in \cite{Gonze1997dynamical}, and implemented in \emph{ab initio} materials physics software packages such as \cite{abinit1,abinit2,abinit3}. Here, we develop a unified 
theoretical framework to analyze phonon-polaritons in materials, which can address effects of spatial dispersion as well as effects coming from arbitrary dimensionality. Specifically, we develop a means to arrive at the dielectric function associated with optical phonons in polar materials of arbitrary dimensionality. We pay close attention to develop a description of the optical response that shows clearly the parallels to the description of plasmonic response from first principles. From this theoretical framework, we not only accurately predict surface phonon polaritons in thick materials where a bulk permittivity is valid but also provide tools to predict phonon polariton dispersion in monolayers and anticipate when spatially nonlocal corrections to the phonon contribution to the dielectric function become relevant. We apply this formalism to calculate the dielectric function of silicon carbide and hexagonal boron nitride from first principles, and show that the results agree well with measurements. Finally, we develop the theory of phonon polaritons in a 2D polar material, specifying the dielectric function in terms of \emph{ab initio} parameters, and then finding a universal form for the dispersion relation of 2D phonon polaritons.

>>>>

To address these questions an \emph{ab initio} framework to predict the phonon contribution to the dielectric tensor in arbitrary settings is essential. Methodologies exist to calculate the local permittivity contribution from phonons in a 3D bulk, as in \cite{Gonze1997dynamical}, and are implemented in \emph{ab initio} materials physics software packages\cite{abinit1,abinit2,abinit3}. Here, we develop a unified 
theoretical framework to analyze phonon-polaritons in materials, which can address effects of spatial dispersion as well as effects that emerge from arbitrary dimensionality. Specifically, we develop a means to arrive at the dielectric function associated with optical phonons in polar materials of arbitrary dimensionality. We pay close attention to develop a description of the optical response that shows clearly the parallels to the description of plasmonic response from first principles. Importantly, from this theoretical framework, we not only accurately predict surface phonon polaritons in thick materials where a bulk permittivity is valid but also provide tools to predict phonon polariton dispersion in monolayers and anticipate when spatially nonlocal corrections to the phonon contribution to the dielectric function become relevant. We apply this formalism to calculate the dielectric function of silicon carbide and hexagonal boron nitride from first principles, and show that the results agree well with measurements. Finally, we develop the theory of phonon polaritons in a 2D polar material, specifying the dielectric function in terms of \emph{ab initio} parameters, and then finding a universal form for the dispersion relation of 2D phonon polaritons.
